CS6601 - Fall 2017 \\ Project 2

### 2017-10-20 Project2/LaTeX/report.tex
Report?
Added plus 1 to report

	For the threshold value, it is assumed that the number of bits will be no greater than the max number of bits that the dot product can take. The formula used to calculate the max number of bits for the dot product is shown in Equation \ref{equ:bits}.

@@

>>>>

	For the threshold value, it is assumed that the number of bits will be no greater than the max number of bits plus 1 that the dot product can take. The formula used to calculate the max number of bits for the dot product is shown in Equation \ref{equ:bits}.

@@

	All inputs are assumed to be unsigned integers as required by the project description.
